When are Fuzzy Extractors Possible?

### 2015-02-10 info-bounds/FuzzyExtPossibility.tex
minor edits to intro

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key. A minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret, because the fuzzy extractor converts such a guess to the key.
We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.  Fuzzy min-entropy measures the success of the adversary when provided with the functionality of the fuzzy extractor.  It measures the \emph{ideal} security of a distribution.

High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required (assuming the existence of semantically-secure graded encodings). Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy. The challenge is to design information-theoretic fuzzy extractors whose security (almost) matches the fuzzy min-entropy of a distribution.

In this work, we ask whether this challenge is inherent.
 We provide two main technical results.
\begin{itemize}
\item \textbf{Sufficiency of fuzzy min-entropy:}  It is possible to build a fuzzy extractor for any \emph{precisely known} physical source.  This result justifies fuzzy min-entropy as the right measure of the quality of a noisy distribution for key derivation.  Previous results considered the entropy and error tolerance of a separately and had not secured many sources with fuzzy min-entropy.
\item \textbf{Cost of distributional uncertainty:}  High entropy distributions can never be fully observed and must be modeled.  An adversary may have a better model than the fuzzy extractor designer.  To compensate, fuzzy extractors are typically designed to work for families of physical sources. We show that this uncertainty is an impediment to security by building a family of high fuzzy min-entropy sources for which no fuzzy extractor can exist.  This result justifies further study of physical sources to increase the fidelity of our models.
\end{itemize}
We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.  Our results are information-theoretic, but we discuss implications for the computational setting.

@@

\newpage
%\tableofcontents\newpage

@@

The noninteractive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}, which consists of two algorithms.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.   T
The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces an output $\key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.   The correctness guarantee is that the key is reproduced precisely as long as the distance between $w$ and $w'$ is at most $t$.

@@

Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.  Superlogarithmic fuzzy min-entropy  is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition).  Fuzzy min-entropy measures the maximum obtainable key from a noisy distribution.  
However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.\footnote{For nearly uniform distributions, $\Hfuzz(W) \approx \Hoo(W)- \log |B_t|$.  In this setting, standard coding based constructions of fuzzy extractors (instantiated with optimum codes) yield keys of size approximately $\Hfuzz(W)$.}  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}.

We answer this question in two important settings.  An important aspect of a fuzzy extractor is how much it knows about the target distribution $W$.  In the extreme the fuzzy extractor has a complete description of the probability density function of $W$.  We call this setting the \emph{known distribution} setting.  (Previous works have consider

Assuming full knowledge of a distribution is often unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors). Thus, the design is fixed with a partially known distribution, and the adversary may therefore know more about the distribution than the designer of the fuzzy extractor.  We call this setting \emph{family of distributions}.
We ask whether fuzzy min-entropy is sufficient in each of these settings.

\paragraph{Sufficiency of $\Hfuzz(W)$ for a Known Distribution}
We show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a \emph{known distribution} $W$.  It is important to emphasize that these constructions incorporate the knowledge of the complete distribution of $W$ (and, in particular, they are not polynomial-time).

A number of previous works in this known-distribution setting have provided efficient algorithms and
tight bounds for specific distributions---generally the uniform distribution or
i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
Our characterization may be seen as unifying previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.

\paragraph{Impossibility of a Fuzzy Extractor for a Family of Distributions}
Our results are negative when the distribution $W$ is only known to come from a family $\mathcal{W}_Z$ (\thref{thm:imposs fuzz ext}).
Specifically, we show a family of distributions $\mathcal{W}_Z$ such that not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.  We emphasize that each distribution $W_z\in \mathcal{W}_Z$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W_z)=\Hoo(W_z)$, because all points in $W_z$ are distance at least $t$ apart. Our proof relies on high dimensionality of each $W_z$ and on perfect correctness of the $\rep$ procedure.
This result shows that uncertainty in the distribution $W$ is devastating to building a fuzzy extractor.  This result motivates the further research into physical sources.  \bnote{come back to this sentence}

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Known Distribution & Family of Distributions\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext})\\
\hline
Secure Sketch & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs sketch})
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a superlogarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}

@@

\bnote{asked to discuss implications of our negative results}
\bnote{can we reframe the paper as the cost of distributional uncertainty?}
\bnote{compare to current constructions?}
\subsection{Our Techniques}

\paragraph{Techniques for Positive Results for Known Distributions} We now explain how to construct a secure sketch for an arbitrary known distribution $W$ (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).   Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz(W)$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ``levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

\paragraph{Techniques for Negative Results for Distribution Families}
We construct a family of distributions $\mathcal{W}_Z$ and prove impossibility for a uniformly random $W_z \leftarrow \mathcal{W}_Z$~(instead of proving impossibility for a worst-case $W_z$).
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W_z\leftarrow \mathcal{W}_Z$ and $w\leftarrow W_z$), while
the adversary knows $W_z$.   To exploit the asymmetry, we construct $\mathcal{W}_Z$ so that conditioning on the knowledge of $W_z$~(the outcome $z$) reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.

Then we show how the adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
In the secure sketch case, $ss$ can be used to find fixed points of $\rec(\cdot, ss)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$. This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.

@@

The result for fuzzy extractors is delicate.  It uses the fact that $p$ partitions the space into nonoverlapping regions, which is implied by perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem. It also uses the fact that there are few points far from the boundary of every region, which is implied by the geometry of  the high-dimensional Hamming space.  This fact seems crucial: in contrast, in low-dimensional Euclidean space, which does not have this property, a single fuzzy extractor can work for any distribution with sufficient $\Hfuzz$. (Such a construction would use quantization or tiling, similar to, for example, \cite{CK03,LT03,CZC04,LC06,BDHTV10,VTOSS10}.  Each sample from $W$ would map to the ``tile'' containing it, from which the output key would be extracted. A randomly chosen quantizer would have the property that few samples lie near the boundary, giving almost-perfect correctness; if perfect correctness is desired, we can give up on security for those rare samples and simply use a special value of $p$ to indicate that one of them was the input.)

\subsection{Related Settings}
\label{sec:related settings}
\paragraph{Other settings with close readings:  $\Hfuzz$ is sufficient}
The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.   In this computational setting, fuzzy extractors and secure sketches can be constructed for the family of all distributions $W$ with superlogarithmic $\Hfuzz$ by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}. The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.  In addition to relying on strong assumptions for security (namely, the existence of semantically-secure multilinear maps), this construction is not of practical efficiency. Note that if this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).

@@

\paragraph{Correlated rather than close readings}
A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.   This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.  We compare our positive results to these characterizations in \apref{sec:corr variables}.  To the best of our knowledge, prior results on correlated random variables are in the known distribution setting, we are unaware of works that consider security for a family of distributions.

%The definition of $\Hfuzz$ can be extended to this model (by again thinking of the adversary as choosing the value $w'$ that is most likely to lead to a success).

\paragraph{Organization} The remainder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor for each known distribution with fuzzy min-entropy.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we provide negative results  for families of distributions for secure sketches and fuzzy extractors, respectively.

@@

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}
\noindent
Fuzzy min-entropy is a necessary condition for security.  It measures the advantage provided to the adversary by allowing them to run the $\rep$ functionality.  Thus, the fuzzy min-entropy is the ideal security that any fuzzy extractor should be compared against.  All proofs for statements in this section can be found in \apref{sec:proof fuzz necessary}.
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution  over $(\mathcal{M}, \dis)$ with $\Hfuzz(W) =m$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, W, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$.  Then 
\[
\epsilon\ge 2^{-m}-\delta -2^{-\kappa}.
\]
In particular, for security parameter $n$, if $m = \Theta(\log n), \delta = \ngl(n), \kappa = \omega(\log n)$, then $\epsilon  = 1/\poly(n)$.
%If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-fuzzy extractor %that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$
% with error $\delta = \ngl(n)$ for $\kappa =\omega(\log n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
The proof of \propref{prop:fuzz necessary} is not specific to the fuzzy extractor setting, it also applies to computational and interactive definitions.  There are many distributions with $\Hfuzz$ with no known fuzzy extractor~(or corresponding impossibility result).
Our goal is to provide a superlogarithmic length key whenever a distribution has superlogarithmic fuzzy min-entropy. 
Fuzzy min-entropy obeys some natural entropy properties:
\begin{lemma}
\label{lem:conditional fuzz rule}
$\Hfuzz(W|P=p) \ge \Hfuzz(W) + \log \Pr[P=p]$.
\end{lemma}

@@

\section{Sufficiency of $\Hfuzz(W)$ When the Algorithms Know the Distribution}
\label{sec:known distributions}
In this section, we show it is possible to build known-distribution secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.
%\subsection{Well-Spread Distributions}
%\bnote{can remove this section if we need space}
%We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Error-correction is ``easy'' when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points.  %Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  
%We begin by defining a well-spread distribution.
%
%\begin{definition}
%A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
%\end{definition}
%Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has superlogarithmic min-entropy).  Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result is intuitive.  However, our negative results for the family of distributions setting will be for families of well-spread distributions.  This result illustrates how different the known distribution and family of distributions settings are.}
%\begin{lemma}
%\label{lem:nosketchwellspread}
%Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, W, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.  In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.  \rec is efficient if there exists efficient decoding for the points in $W$.  By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, W,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
%\end{lemma}  
%\begin{proof}
%It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.  Since $W$ is $t_{cor}$-well spread, for all $w_0, w_1 \in W, \dis (w_0, w_1)\ge t_{cor}$.  Then by the triangle inequality,
%\[
%t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
%This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
%\end{proof}

@@

In the previous section, we showed the sufficiency of $\Hfuzz(W)$ for known distribution algorithms.  Unfortunately, it is unrealistic to assume that $W$ is completely known.  Traditionally, algorithms deal with this uncertainty by providing security for a family of distributions $\mathcal{W}$.

>>>>

\begin{abstract}
Fuzzy extractors (Dodis et al., Eurocrypt 2004) convert repeated noisy readings of a high-entropy secret into the same uniformly distributed key. A minimum condition for the security of the key is the hardness of guessing a value that is similar to the secret, because the fuzzy extractor converts such a guess to the key.
We define \emph{fuzzy min-entropy} to quantify this property of a noisy source of secrets.  Fuzzy min-entropy measures the success of the adversary when provided with \emph{only} the functionality of the fuzzy extractor, that is, the \emph{ideal} security possible from a noisy distribution.

High fuzzy min-entropy is necessary for the existence of a fuzzy extractor; moreover, there is evidence that it may be sufficient when only computational security is required. Nevertheless, information-theoretic fuzzy extractors are not known for many practically relevant sources of high fuzzy min-entropy. In this work, we ask whether this challenge is inherent.  We show the following:
\begin{itemize}
\item \textbf{Sufficiency of fuzzy min-entropy:}  We construct a fuzzy extractor for each physical source with fuzzy min-entropy.  This result justifies fuzzy min-entropy as the right measure of the quality of a noisy distribution for key derivation.  Previous results considered the entropy and error tolerance of a separately and had not secured many sources with fuzzy min-entropy.  
The constructed fuzzy extractor must \emph{precisely know} the distribution of the noisy source.
\item \textbf{Cost of distributional uncertainty:}  High entropy sources can never be fully observed and must be modeled.  An adversary may have a better model than the fuzzy extractor designer.  To compensate, fuzzy extractors are typically designed to work for families of physical sources. We build a family of high fuzzy min-entropy sources which no fuzzy extractor can secure.  This result emphasizes the importance of high fidelity models of high entropy sources.
\end{itemize}
We provide similar but stronger results for secure sketches, whose goal is not to derive a consistent key, but to recover a consistent reading of the secret.  Our results are information-theoretic, but we discuss implications for the computational setting.

@@

@@

The noninteractive setting is modeled by a primitive called a fuzzy extractor~\cite{DBLP:journals/siamcomp/DodisORS08}, which consists of two algorithms.  %Consider some distribution $W$.%The goal of a fuzzy extractor is to derive stable keys from a distribution $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.   T
The  generate algorithm ($\gen$)  takes an initial reading $w$ and produces an output $\key$ along with a nonsecret helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $\key$.   The correctness guarantee is that the key is reproduced precisely when the distance between $w$ and $w'$ is at most $t$.

@@

Fuzzy min-entropy measures the quality of a distribution when provided oracle access to the functionality of a fuzzy extractor.  Fuzzy min-entropy measures the ideal security of a noisy source of entropy when used for key derivation, similar to distributional notions of program obfuscation~\cite{barak2001possibility,DBLP:conf/stoc/DodisS05,DBLP:conf/tcc/DodisS05}---we discuss the connection in \secref{sec:related settings}.  Superlogarithmic fuzzy min-entropy is \emph{necessary} for nontrivial key extraction~(\propref{prop:fuzz necessary} formalizes the above intuition).

However, existing constructions do not measure their security in terms of fuzzy min-entropy; instead, their security is shown to be  $\Hoo(W)$ minus some loss that is at least $\log |B_t|$ due to error-tolerance. Since $\Hoo(W)-\log |B_t| \le \Hfuzz(W)$, it is natural to ask whether this loss is necessary. This question is particularly relevant when the gap between the two sides of the inequality is high.\footnote{For nearly uniform distributions, $\Hfuzz(W) \approx \Hoo(W)- \log |B_t|$.  In this setting, standard coding based constructions of fuzzy extractors (instantiated with optimum codes) yield keys of size approximately $\Hfuzz(W)$.}  As an example, iris scans appear to have significant $\Hfuzz(W)$ (because iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing}) but negative $\Hoo(W) -\log |B_t|$ \cite[Section 5]{blanton2009biometric}. We therefore ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?} There is evidence that it may be when the security requirement is computational rather than information-theoretic---see \secref{sec:related settings}. We provide an answer in two settings.

\paragraph{Sufficiency of $\Hfuzz(W)$ for a Precisely Known Distribution}
Ideally, a fuzzy extractor has \emph{precise knowledge} of the probability distribution function of $W$.  We call this  the \emph{precise knowledge} setting.  In this setting, we show that for every source $W$ with superlogarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a superlogarithmic length $\key$ (\corref{cor:extension to fuzz ext}). Our construction crucially utilizes the probability distribution function of $W$ and, in particular, is not polynomial time.  This result shows that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor of a distribution $W$.

A number of previous works in the precise knowledge setting have provided efficient algorithms and
tight bounds for specific distributions---generally the uniform distribution or
i.i.d. sequences (for example, \cite{JW99,LT03,DBLP:conf/eccv/TuylsG04,hao2006combining,DBLP:journals/corr/abs-1112-5630,IgnatenkoW2012}). 
Our characterization unifies previous work, and justifies using $\Hfuzz(W)$ as the measure of the quality of a noisy distribution,  rather than cruder measures such as $\Hoo(W)-\log |B_t|$.

\paragraph{The Challenge of Precisely Distributional Knowledge}
Assuming \emph{precise knowledge} of a distribution $W$ may be unrealistic. Indeed, high-entropy distributions can never be fully observed directly and must therefore be modeled. It is imprudent to assume that the designer's model of a distribution is completely accurate---the adversary, with greater resources, would likely be able to build a better model. Therefore, fuzzy extractor designs cannot usually be tailored to one  particular source. Existing designs work for a family of sources (for example, all sources of min-entropy at least $m$ with at most $t$ errors). Thus, the design is fixed with a partially known distribution, and the adversary may know more about the distribution than the designer of the fuzzy extractor.  We call this the \emph{distributional uncertainty} setting.

\paragraph{The Cost of Distributional Uncertainty}
When the distribution is $W$ is uncertain, our results are negative.   In this setting, $W$ is known to be an element of a family of distributions $\mathcal{W}_Z$.
We construct a family $\mathcal{W}_Z$ where not even a 2-bit fuzzy extractor can be secure for most distributions in  $\mathcal{W}_Z$.  We emphasize that each distribution $W_z\in \mathcal{W}_Z$ has superlogarithmic fuzzy min-entropy---in fact, $\Hfuzz(W_z)=\Hoo(W_z)$, because all points in $W_z$ are distance at least $t$ apart. Our proof relies on high dimensionality of each $W_z$ and on perfect correctness of the $\rep$ procedure.
This result shows that uncertainty in the distribution $W$ is devastating to building a fuzzy extractor.  In particular, our positive results (\corref{cor:extension to fuzz ext}) show it is possible to build a fuzzy extractor for each $W_z$, but no construction can simultaneously secure the whole family.  Our result motivates further research into high fidelity descriptions of noisy sources.

\begin{table}[h]
\begin{center}
\begin{tabular}{c  l l }
 & Precise Knowledge & Distributional Uncertainty\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext})\\
\hline
Secure Sketch & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs sketch})
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract an information-theoretic superlogarithmic length key?}
\label{tab:main results}
\end{table}

@@

\paragraph{Interpreting our Results}
Our results show that fuzzy min-entropy is sufficient for noisy key derivation if the distribution is precisely known but insufficient if the distribution is only known to come from a family.  A similar situation occurs in the (noiseless) randomness extraction literature~\cite{nisan1993randomness}.  Deterministic randomness extractors are possible if the distribution is precisely known, but impossible for all high min-entropy distributions~\cite{santha1986generating}.  This impossibility can be overcome by the use of a short seed of uniform randomness.  
We must find an analogous relaxation to derive keys from noisy sources.  One natural relaxation is providing security against only  computationally bounded adversaries, see \secref{sec:related settings}.

\subsection{Our Techniques}

\paragraph{Techniques for Positive Results for a Precisely Known Distribution} We now explain how to construct a secure sketch for a precisely known distribution $W$ with fuzzy min-entropy (we already explained how to construct a fuzzy extractor from it).  We begin with distributions in which all points in the support have the same probability (so-called ``flat'' distributions).   Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must disambiguate which point $w\in W$ within distance $t$ of $w'$ was sketched. Disambiguating multiple points can be accomplished by universal hashing, as long as the size of hash output space is slightly greater than the number of possible points. Thus, our sketch is computed via a universal hash of $w$. To determine the length of that sketch, consider the heaviest (according to $W$) ball of radius $t$. Because the distribution is flat, it is also the ball with the most points of nonzero probability. Thus, the length of the sketch needs to be slightly greater than the logarithm of the number of non-zero probability point in that ball. Since $\Hfuzz(W)$ is determined by the weight of that ball, the number of points cannot be too high and there will be entropy left after the sketch is published.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points, because there could be too many low-probability points in a single ball despite a high $\Hfuzz(W)$.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call ``levels.''  We then write down, as part of the sketch, the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}~(\consref{cons:leveling}).

\paragraph{Techniques for Negative Results for Distributional Uncertainty}
We construct a family of distributions $\mathcal{W}_Z$ and prove impossibility for a uniformly random $W_z \leftarrow \mathcal{W}_Z$.
We start by observing the following asymmetry: $\gen$  sees only the sample $w$ (obtained via $W_z\leftarrow \mathcal{W}_Z$ and $w\leftarrow W_z$), while
the adversary knows $W_z$.   To exploit the asymmetry, we construct $\mathcal{W}_Z$ so that conditioning on the knowledge of $W_z$~(the outcome $z$) reduces the distribution to a single affine line, but conditioning on $w$ leaves the rest of the distribution uniform on a large fraction of the entire space.

An adversary can exploit the knowledge of the affine line to reduce the uncertainty about $w$ (in the secure sketch case) or $\key$ (in the fuzzy extractor case). 
In the secure sketch case, $ss$ can be used to find fixed points of $\rec(\cdot, ss)$ which, by the correctness requirement of the sketch, must be separated by minimum distance $t$. This means there aren't too many of them, so few can lie on an average line, permitting the adversary to guess one easily.

@@

The result for fuzzy extractors is delicate.  It uses the fact that $p$ partitions the space into nonoverlapping regions, which is implied by perfect correctness.  Extending this result to imperfect correctness seems challenging and is an interesting open problem. Our result also uses the fact that there are few points far from the boundary of every region, which is implied by the geometry of  the high-dimensional Hamming space.  This fact seems crucial: in contrast, in low-dimensional Euclidean space, which does not have this property, a single fuzzy extractor can work for any distribution with sufficient $\Hfuzz$. (Such a construction would use quantization or tiling, similar to, for example, \cite{CK03,LT03,CZC04,LC06,BDHTV10,VTOSS10}.  Each sample from $W$ would map to the ``tile'' containing it, from which the output key would be extracted. A randomly chosen quantizer would have the property that few samples lie near the boundary, giving almost-perfect correctness; if perfect correctness is desired, we can give up on security for those rare samples and simply use a special value of $p$ to indicate that one of them was the input.)

\subsection{Related Settings}
\label{sec:related settings}
\paragraph{Other settings with close readings:  $\Hfuzz$ is sufficient}
The security definition of fuzzy extractors and secure sketches can be weakened to protect only against computationally bounded adversaries~\cite{fuller2013computational}.   In this computational setting, a single fuzzy extractor (or secure sketch) can simultaneously secure all possible distributions by using virtual grey-box obfuscation for all circuits~\cite{BitanskyCKP14}. The construction places into $p$ the obfuscated program for testing proximity to $w$ and outputting the appropriate value if the test passes.\footnote{If this construction is used for a secure sketch, $W$ will remain unpredictable conditioned on $p$, but will not have pseudoentropy (see  \secref{sec:feas comp sec sketch} for details).}  This construction is secure when the adversary can rarely learn \key with oracle access to the program functionality.  The set of distributions with fuzzy min-entropy are exactly those where an adversary learns \key with oracle access to the functionality with negligible probability. Thus, extending our negative result to the computational setting would rule out the existence of semantically-secure multilinear maps.

@@

\paragraph{Correlated rather than close readings}
A different model for the problem of key derivation from noisy sources does not explicitly consider the distance between $w$ and $w'$, but rather views $w$ and $w'$ as samples of drawn from a correlated pair of random variables.   This model is considered in multiple works, including~\cite{wyner1975wire,DBLP:journals/tit/CsiszarK78,DBLP:journals/tit/AhlswedeC93,DBLP:journals/tit/Maurer93}; recent characterizations of when key derivation is possible in this model include \cite{DBLP:conf/asiacrypt/RennerW05} and \cite{DBLP:journals/corr/TyagiW14}.  We compare our positive results to these characterizations in \apref{sec:corr variables}.  To the best of our knowledge, prior results on correlated random variables are in the precise knowledge setting, we are unaware of works that consider the cost of distributional uncertainty.

\paragraph{Organization} The remainder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:known distributions}, we construct a fuzzy extractor in the precise knowledge setting.  In Sections~\ref{sec:family of dist} and~\ref{sec:imposs fuzz ext} we construct families of distributions that no secure sketches and fuzzy extractors can secure, respectively~(the distributional uncertainty setting).

@@

\begin{definition}
\label{def:fuzzy min-ent}
The $t$-fuzzy min-entropy of a distribution $W$ in a metric space $(\mathcal{M}, \dis)$ is:
\[
\Hfuzz(W) = -\log \left(\max_{w'}  \sum_{w\in W | \dis(w, w')\le t} \Pr[W=w] \right)
\]
\end{definition}
\noindent
Fuzzy min-entropy is a necessary condition for security.  It measures the advantage provided to the adversary by allowing them to run the $\rep$ functionality.  Thus, the fuzzy min-entropy is the ideal security that any fuzzy extractor should be compared against.  We defer proofs of statements in this section to \apref{sec:proof fuzz necessary}.
\begin{proposition}
\label{prop:fuzz necessary}
Let $W$ be a distribution  over $(\mathcal{M}, \dis)$ with $\Hfuzz(W) =m$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \{W\}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$.  Then 
\[
\epsilon\ge 2^{-m}-\delta -2^{-\kappa}.
\]
In particular, for security parameter $n$, if $m = \Theta(\log n), \delta = \ngl(n), \kappa = \omega(\log n)$, then $\epsilon  = 1/\poly(n)$.
\end{proposition}

%Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
%\lemref{lem:fuzz necessary} still applies.  
The proof of \propref{prop:fuzz necessary} is not specific to the fuzzy extractor setting, it also applies to computational and interactive definitions.  Fuzzy min-entropy represents an upper bound on the security from a noisy source.  In the \secref{sec:related settings} computational setting there is evidence it may be possible to (nearly) achieve this upper bound.  However, in the information-theoretic setting there are many distributions with fuzzy min-entropy with no known fuzzy extractor~(or corresponding impossibility result).  We know show some properties of fuzzy min-entropy.
\begin{lemma}
\label{lem:conditional fuzz rule}
$\Hfuzz(W|P=p) \ge \Hfuzz(W) + \log \Pr[P=p]$.
\end{lemma}

@@

\section{Sufficiency of $\Hfuzz(W)$ in the Precise Knowledge Setting}
\label{sec:known distributions}
In this section, we show it is possible to build secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) given precise knowledge of a distribution $W$ whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider flat distributions and then turn to arbitrary distributions.

@@

In the previous section, we showed the sufficiency of $\Hfuzz(W)$ when the distribution was precisely known.  It may be infeasible to completely characterize a high entropy distribution $W$.  Traditionally, algorithms deal with this \emph{distributional uncertainty} by providing security for a family of distributions $\mathcal{W}_Z$.
